Tidal field anisotropy as a tracer of cosmic voids

### 2015-01-10 cosmic_voids.tex
Changing units of void size function

Once defined our method to classify bulk voids based upon web 
classification schemes of the cosmic web, we proceed to analyse some 
physical properties in order to compare their consistency with the 
geometry of voids as quantified by our method and by density-based schemes.
Next, through the reduced inertia tensor we quantify the shape distribution 
of voids. Finally, we compute numerical radial profiles of density and 
peculiar velocity of bulk voids.

%-------------------------------------------------------------------------
\subsection{Statistics of halos in voids}
\label{subsec:shape_voids}
%-------------------------------------------------------------------------

One of the main challenges in observational void finding is the discrete 
nature of galaxy surveys

 we calculate contours of discrete fields like the median mass and 
the local number of local dark matter halos and

, like the inertia values,
the density and peculiar velocities profiles as calculated over the grid 
and profiles of number of halos.

>>>>

%-------------------------------------------------------------------------
\subsection{The void size distribution}
\label{subsec:shape_voids}
%-------------------------------------------------------------------------
